More than one Author with different Affiliations

### 2012-05-16 paper/ms.tex
Random minor edits

\title{Probabilistic Catalogues from Crowded Star Fields}
\author[1,2]{Brendon J. Brewer}
\author[3]{David W. Hogg}
\author[3]{Daniel Foreman-Mackey}
\affil[1]{UCSB}
\affil[2]{Auckland}
\affil[3]{NYU}

@@

@@

\subsection{Future Possibilities}
{\bf Hogg}: {\it I think this problem is important enough and general enough
that we should spend some time working on some ideas there.  If we can sample
over image explanations, our powers in astronomy will be awesome
beyond our wildest imaginings.}

\subsection{Genetic Moves}
Here I will sketch some ideas...

@@

\end{thebibliography}

>>>>

\title{Probabilistic Catalogues from Crowded Star Fields}
\author[1,2]{Brendon J. Brewer}
\author[3]{David W. Hogg}
\author[3]{Daniel Foreman-Mackey}
\affil[1]{\small Dept. of Physics, University of California, Santa Barbara, CA 93106, USA}
\affil[2]{Department of Statistics, University of Auckland, Private Bag 92019, Auckland, New Zealand
}
\affil[3]{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY, 10003, USA
}

@@

\citep{massinf}

@@

%\subsection{Future Possibilities}
%{\bf Hogg}: {\it I think this problem is important enough and general enough
%that we should spend some time working on some ideas there.  If we can sample
%over image explanations, our powers in astronomy will be awesome
%beyond our wildest imaginings.}

%\subsection{Genetic Moves}
%Here I will sketch some ideas...

@@

\bibitem[\protect\citeauthoryear{Skilling}{1998}]{massinf} 
Skilling J., 1998, Massive Inference and Maximum Entropy, in Maximum Entropy 
and Bayesian Methods, Kluwer Academic Publishers, Dordrecht/Boston/London p.14
\end{thebibliography}
